### 2017-07-17 Tran Nott Kohn/outline.tex
PF work
ffs

\subsection{Randomised Quasi Monte Carlo}
Randomised Quasi Monte Carlo (Matousek 1998; Sobol 196X, GTN 2017).

@@

\subsection{Natural Gradients}

lower dimension 
analytical for some distributions eg. MVN

Natural Gradients  (Amari 1998, Hoffman et al. 2013).

@@

don't need to particle filter after every iteration

@@

\section{Appendix}
\subsection{Inverse Fisher Matrix}

>>>>

\subsection{Randomised Quasi Monte Carlo}
Randomised Quasi Monte Carlo (Matousek 1998; Sobol 196X, Gunawan, Tran and Kohn 2017).

@@

@@

@@
